%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This document is based on a template available at
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{amssymb}
\usepackage{url}

%\input{officialheader.tex} %If you want this file to compile to my CV, comment out this line and uncomment the next three
\name{Amelia A. McNamara} 
\address{\url{amcnamara@smith.edu} \\ \url{www.science.smith.edu/~amcnamara}  \\ @AmeliaMN } 
\address{215 Burton Hall \\ Smith College \\ Northampton MA, 01063 \\ (413) 585-3851 } 


\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{McNamara, page \thepage\ of \pageref{LastPage}}
\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Preparation}
{\bf Macalester College}  \hfill St. Paul, MN \\
{\bf B.A., Mathematics} and {\bf English}  \hfill  2010 \\ \smallskip 

{\bf University of California - Los Angeles} \hfill Los Angeles, CA \\
{\bf Ph.D., Statistics} \hfill 2015\\ 


\end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC APPOINTMENTS
%----------------------------------------------------------------------------------------


\begin{rSection}{ Appointments}
{\bf Visiting Assistant Professor} \hfill {2015-2019} \\
{Smith College Program in Statistical and Data Science}\hfill {Northampton, MA} \\
\end{rSection}


%----------------------------------------------------------------------------------------
%	PAPERS
%----------------------------------------------------------------------------------------

\begin{rSection}{Products}

{\bf \em{McNamara, A.}} {\bf Key attributes of a modern statistical computing tool. } (submitted) \\
URL: \url{https://arxiv.org/abs/1610.00985}

{\bf \em{McNamara, A.}} {\bf On the state of computing in statistics education: Tools for learning and for doing. } (in review) URL: \url{https://arxiv.org/abs/1610.00984}

{\bf \em McNamara, A.} {\bf Considering the gap between learning and doing statistics.} {\em International Handbook of Research in Statistics Education.} In chapter 15, The Future of Research in Statistics Education. (in revision) 

{\bf \em McNamara, A.} {\bf Barriers and opportunities for nurturing statistical thinking before college}{ \em CHANCE,} Vol. 28, Issue 4. (2015). URL: \url{http://dx.doi.org/10.1080/09332480.2015.1120126}

{\bf \em McNamara, A. }and Hansen, M. {\bf Teaching data science to teenagers.}{ \em Proceedings of the 9th International Conference on Teaching Statistics.} (2014). URL: \url{http://icots.info/9/proceedings/pdfs/ICOTS9_9C2_MCNAMARA.pdf}

\end{rSection}


%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------

\begin{rSection}{Synergistic Activities}


\begin{sSubsection}{Data Science for Statisticians}{ (short course)}{March 2017}{ENAR, International Biometric Society}{Washington, DC}
\end{sSubsection}

\begin{sSubsection}{Introduction to R }{ (short course, with C. Jones)}{March 2016}{NICAR, Investigative Reporters \& Editors Conference}{Denver, CO}
\end{sSubsection}

\begin{sSubsection}{Youth, Learning and Data Science Summit}{ (invited participant)}{August 2016}{University of California, Berkeley}{Berkeley, CA}
\end{sSubsection}

\begin{sSubsection}{Teaching Integrity in Empirical Research Workshop}{ (faculty fellow)}{June 2016}{Haverford College}{Haverford, PA}
\end{sSubsection}

\end{rSection}









\end{document}
